A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-20 manuscript.Rmd
fixes missing slash

To use `docker` you need to start Docker Desktop. In the settings of Docker Desktop, you have to allow the sharing of your drive. Docker on Windows requires the path to be special; therefore, you need to hand-edit the `Makefile` and set `current_path` to the current directory and use `make all DOCKER=TRUE WINDOWS=TRUE`. We hope that future releases of Docker for Windows will not require that workaround.

>>>>

To use `docker` you need to start Docker Desktop. In the settings of Docker Desktop, you have to allow the sharing of your drive. Docker on Windows requires an unusual path specification (e.g., `C:\\Users\\aaron\\Documents\\reproducible-research` becomes `/c/Users/aaron/Documents/reproducible-research`). Therefore, you currently need to hand-edit the `Makefile` and set `current_path` to the project directory and use `make all DOCKER=TRUE WINDOWS=TRUE`. We hope that future releases of Docker for Windows will not require that workaround.
